Final Report

### 2022-05-06 Final Report.Rmd
some changes
popultion graphs

>>>>

This is a closer view on the population growth over time in both the high and low populated countries that we selected.
```{r, echo=FALSE}
pop_high_growth<- ggplot(data=joined_high, aes(x=year, y=Count, color=country)) +
  geom_line() +
  labs(title="Population Over Time in High Populated Countries")+
  xlab("Year")+
  ylab("Population")
ggplotly(pop_high_growth)

pop_low_growth<- ggplot(data=joined_low, aes(x=year, y=Count, color=country)) +
  geom_line() +
  labs(title="Population Over Time in Low Populated Countries")+
  xlab("Year")+
  ylab("Population")
ggplotly(pop_low_growth)
```
